Hydras \& Co.

### 2022-03-10 doc/chapter-powers.tex
fix a bug (snippet)

In addition to this big computation time, this approach 
generates a huge proof term. Just try to execute the command 
``\texttt{Print C87\_ok}'' to get a measure of its size.
In order to understand this poor performance, let us consider an intermediate
subgoal of the previous proof generated after a sequence of unfoldings and simplifications. This goal is presented below.
\begin{figure}[h]
  \centering
\inputsnippets{Addition_Chains/WhySoSlow}  
  \caption{A big goal}
  \label{fig:big-goal}
\end{figure}

>>>>

In addition to this big computation time, this approach 
generates a huge proof term. Just try to execute the command 
``\texttt{Print C87\_ok}'' to get a measure of its size.
In order to understand this poor performance, let us consider an intermediate
subgoal of the previous proof generated after a sequence of unfoldings and simplifications. This goal is presented in Figure~\vref{fig:big-goal}.

\begin{figure}[h]
  \centering
  \begin{Coqanswer}
    1 goal (ID 506)

  A : Type
  E_op : Mult_op A
  E_one : A
  E_eq : Equiv A
  M : EMonoid E_op E_one E_eq
  x : A
  ============================
  E_eq
    (x * x * x * (x * x * x) * x * (x * x * x) *
     (x * x * x * (x * x * x) * x * (x * x * x)) *
     (x * x * x * (x * x * x) * x * (x * x * x) *
      (x * x * x * (x * x * x) * x * (x * x * x))) *
     (x * x * x * (x * x * x) * x * (x * x * x) *
      (x * x * x * (x * x * x) * x * (x * x * x)) *
      (x * x * x * (x * x * x) * x * (x * x * x) *
       (x * x * x * (x * x * x) * x * (x * x * x)))) *
     (x * x * x * (x * x * x) * x))
    (x *
     (x *
      (x *
       (x *
        (x *
         (x *
          (x *
           (x *
            (x *
             (x *
              (x *
               (x *
                (x * (x * (x *  ...)))))))))))))))

  \end{Coqanswer}
%\inputsnippets{Addition_Chains/WhySoSlow}  
  \caption{A big goal}
  \label{fig:big-goal}
\end{figure}
